Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-15 prop_letter.tex
prop_letter.tex \section{Convexity} Added a comment...

and [x,y] is NOT included in [z,w]

>>>>

and $[x,y]$ is NOT included in $[z,w]$

\yutsung{{Consider a four dimensional Hilbert space with an orthonormal
basis}~$\Omega=\{\ket{0},\ket{1},\ket{2},\ket{3}\}$, and the commuting
sub-event space~$\events'=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$.
Then, $\bar{\mu}_{0}:\events'\rightarrow\mathscr{I}$ defined by\begin{subequations}
\begin{eqnarray}
 &  & \imposs=\bar{\mu}_{0}(\mathbb{0})\textrm{ ,}\\
 &  & \necess=\bar{\mu}_{0}(\mathbb{1})\textrm{ ,}\\
 &  & \begin{aligned}\unlikely & =\bar{\mu}_{0}(\proj{j})=\bar{\mu}_{0}(\proj{0}+\proj{1})\\
 & =\bar{\mu}_{0}(\proj{0}+\proj{2})\\
 & =\bar{\mu}_{0}(\proj{1}+\proj{2})\textrm{ ,}
\end{aligned}
\\
 &  & \begin{aligned}\likely & =\bar{\mu}_{0}(\mathbb{1}-\proj{j})=\bar{\mu}_{0}(\proj{0}+\proj{2})\\
 & =\bar{\mu}_{0}(\proj{1}+\proj{3})\\
 & =\bar{\mu}_{0}(\proj{2}+\proj{3})
\end{aligned}
\end{eqnarray}
\end{subequations}is an IVPM, where $\ket{j}\in\Omega$ and $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $.
However, $\bar{\mu}_{0}$ is not convex because
\begin{equation}
\begin{aligned} & \bar{\mu}_{0}(\proj{0})+\bar{\mu}_{0}(\mathbb{1}-\proj{3})\\
= & \left[\frac{1}{2},\frac{3}{2}\right]\nsubseteq\left[1,2\right]\\
= & \bar{\mu}_{0}(\proj{0}+\proj{1})+\bar{\mu}_{0}(\proj{0}+\proj{2})\textrm{ .}
\end{aligned}
\end{equation}
}
